Supplement to: An Inception Cohort Study Quantifying How Many Registered Studies are Published.

### 2023-06-18 supplement.Rmd
minor changes

---
title             : "Supplement to: An Inception Cohort Study Quantifying How Many Registered Studies are Published."
shorttitle        : "SUPPLEMENT"
author: 
  - name          : "Eline N. F. Ensinck"
    affiliation   : "1"
    corresponding : no    # Define only one corresponding author
    email         : "e.n.f.ensinck@student.tue.nl"  
  - name          : "Daniël Lakens"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Den Dolech 1, 5600MB Eindhoven, The Netherlands"
    email         : "D.Lakens@tue.nl"
affiliation:
  - id            : "1"
    institution   : "Eindhoven University of Technology"
authornote: |
  This work was funded by VIDI Grant 452-17-013 from the Netherlands Organisation for Scientific Research. The computationally reproducible version of this manuscript is available at https://github.com/Lakens/registered_published and additional materials on https://osf.io/8uqfb/.
abstract: |
  This supplement provides additional details on the classification of registrations as research studies or not, the classification of studies as published or not, additional analyses about how extensive registrations were, and a more fine-grained overview of reasons researchers provided not to publish their study.

@@

We observed quite some variation in the amount of detail in the registrations that we examined. We therefore decided to code the ‘quality’ of the registrations based on the information written in the registration (but not in any associated files, such as uploaded text documents). We labeled all registrations that were empty as 1 (which means it was not clear what the study was about based on the registration) and all registrations that had a minimal description as 2 (this means either a detailed title or small remark about the content of the study was included). If there was a somewhat more detailed but short description about the study, the registration was coded as 3 and finally, all registrations that included a detailed description were coded as 4. In this way, we could compare the quality of the registrations in both groups and check for possible differences that could lead to different publication rates.

@@

Because large differences were observed between the level of detail provided in a registration, and because the level of detail influences the probability that the registration can be matched to a publication of the study, we coded how extensive the registrations were. `r round(100*quality_reg[1,1]/sum(quality_reg[1,]),0)`% of all registrations in the manually opened registrations and `r round(100*quality_reg[2,1]/sum(quality_reg[2,]),0)`% of all registrations in the automatically opened registration were empty, so that it was not clear what the study was about purely from the registration. At least a minimal description was given for `r round(100*quality_reg[1,2]/sum(quality_reg[1,]),0)`% of the registrations in the manually opened registrations and `r round(100*quality_reg[2,2]/sum(quality_reg[2,]),0)`% in the automatically opened registration, meaning that although very brief, there were some details about the content of the study (e.g., a descriptive title). A more detailed short description was provided in `r round(100*quality_reg[1,3]/sum(quality_reg[1,]),0)`% of the cases in the manually opened registrations and `r round(100*quality_reg[2,3]/sum(quality_reg[2,]),0)`% of the cases in the automatically opened registration. Finally, most registrations seem to fall in the last group of extensive registrations (`r round(100*quality_reg[1,4]/sum(quality_reg[1,]),0)`% and `r round(100*quality_reg[2,4]/sum(quality_reg[2,]),0)`% in the manually opened registrations and the automatically opened registration, respectively). These results are summarized in Table \@ref(tab:table-quality). The fact that similar percentages are found in manually opened registrations and the automatically opened registration shows that the level of detail in the registrations does not differ substantially between the two groups. Therefore, the difference in probability that we found a registration that was classified as manually opened, compared to classifications that were automatically opened, is not explained by a difference in the level of detail of the registrations.

>>>>

---
title             : "Supplement to: An Inception Cohort Study Quantifying How Many Registered Studies are Published."
shorttitle        : "SUPPLEMENT"
author: 
  - name          : "Eline N. F. Ensinck"
    affiliation   : "1"
    corresponding : no    # Define only one corresponding author
    email         : "e.n.f.ensinck@student.tue.nl"  
  - name          : "Daniël Lakens"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Den Dolech 1, 5600MB Eindhoven, The Netherlands"
    email         : "D.Lakens@tue.nl"
affiliation:
  - id            : "1"
    institution   : "Eindhoven University of Technology"
authornote: |
  This work was funded by VIDI Grant 452-17-013 from the Netherlands Organisation for Scientific Research. The computationally reproducible version of this manuscript is available at https://github.com/Lakens/registered_published and additional materials on https://osf.io/8uqfb/.
abstract: |
  This supplement provides additional details on the classification of registrations as research studies or not, the classification of studies as published or not, the calculations to extrapolate from our sample to the population of registrations on the OSF before November 2017, additional analyses about how extensive registrations were, and a more fine-grained overview of reasons researchers provided not to publish their study.

@@

@@

We observed quite some variation in the amount of detail in the registrations that we examined. We therefore decided to code the extensiveness of the registrations based on the information written in the registration (but not in any associated files, such as uploaded text documents). We labeled all registrations that were empty as 1 (which means it was not clear what the study was about based on the registration) and all registrations that had a minimal description as 2 (this means either a detailed title or small remark about the content of the study was included). If there was a somewhat more detailed but short description about the study, the registration was coded as 3 and finally, all registrations that included a detailed description were coded as 4. In this way, we could compare the quality of the registrations in both groups and check for possible differences that could lead to different publication rates. `r round(100*quality_reg[1,1]/sum(quality_reg[1,]),0)`% of all registrations in the manually opened registrations and `r round(100*quality_reg[2,1]/sum(quality_reg[2,]),0)`% of all registrations in the automatically opened registration were empty, so that it was not clear what the goal or topic of the study was purely based on the registration. At least a minimal description was given for `r round(100*quality_reg[1,2]/sum(quality_reg[1,]),0)`% of the registrations in the manually opened registrations and `r round(100*quality_reg[2,2]/sum(quality_reg[2,]),0)`% in the automatically opened registration, meaning that although very brief, there were some details about the content of the study (e.g., a descriptive title). A more detailed short description was provided in `r round(100*quality_reg[1,3]/sum(quality_reg[1,]),0)`% of the cases in the manually opened registrations and `r round(100*quality_reg[2,3]/sum(quality_reg[2,]),0)`% of the cases in the automatically opened registration. Finally, most registrations seem to fall in the last group of extensive registrations (`r round(100*quality_reg[1,4]/sum(quality_reg[1,]),0)`% and `r round(100*quality_reg[2,4]/sum(quality_reg[2,]),0)`% in the manually opened registrations and the automatically opened registration, respectively). These results are summarized in Table \@ref(tab:table-quality). The fact that similar percentages are found in manually opened registrations and the automatically opened registration shows that the level of detail in the registrations does not differ substantially between the two groups. Therefore, the difference in probability that we found a registration that was classified as manually opened, compared to classifications that were automatically opened, is not explained by a difference in the level of detail of the registrations.

### 2023-06-18 supplement.tex
minor changes

\abstract{%
This supplement provides additional details on the classification of registrations as research studies or not, the classification of studies as published or not, additional analyses about how extensive registrations were, and a more fine-grained overview of reasons researchers provided not to publish their study.
}

@@

We observed quite some variation in the amount of detail in the registrations that we examined. We therefore decided to code the `quality' of the registrations based on the information written in the registration (but not in any associated files, such as uploaded text documents). We labeled all registrations that were empty as 1 (which means it was not clear what the study was about based on the registration) and all registrations that had a minimal description as 2 (this means either a detailed title or small remark about the content of the study was included). If there was a somewhat more detailed but short description about the study, the registration was coded as 3 and finally, all registrations that included a detailed description were coded as 4. In this way, we could compare the quality of the registrations in both groups and check for possible differences that could lead to different publication rates.

@@

Because large differences were observed between the level of detail provided in a registration, and because the level of detail influences the probability that the registration can be matched to a publication of the study, we coded how extensive the registrations were. 18\% of all registrations in the manually opened registrations and 16\% of all registrations in the automatically opened registration were empty, so that it was not clear what the study was about purely from the registration. At least a minimal description was given for 36\% of the registrations in the manually opened registrations and 28\% in the automatically opened registration, meaning that although very brief, there were some details about the content of the study (e.g., a descriptive title). A more detailed short description was provided in 10\% of the cases in the manually opened registrations and 7\% of the cases in the automatically opened registration. Finally, most registrations seem to fall in the last group of extensive registrations (36\% and 48\% in the manually opened registrations and the automatically opened registration, respectively). These results are summarized in Table \ref{tab:table-quality}. The fact that similar percentages are found in manually opened registrations and the automatically opened registration shows that the level of detail in the registrations does not differ substantially between the two groups. Therefore, the difference in probability that we found a registration that was classified as manually opened, compared to classifications that were automatically opened, is not explained by a difference in the level of detail of the registrations.

>>>>

\abstract{%
This supplement provides additional details on the classification of registrations as research studies or not, the classification of studies as published or not, the calculations to extrapolate from our sample to the population of registrations on the OSF before November 2017, additional analyses about how extensive registrations were, and a more fine-grained overview of reasons researchers provided not to publish their study.
}

@@

@@

We observed quite some variation in the amount of detail in the registrations that we examined. We therefore decided to code the extensiveness of the registrations based on the information written in the registration (but not in any associated files, such as uploaded text documents). We labeled all registrations that were empty as 1 (which means it was not clear what the study was about based on the registration) and all registrations that had a minimal description as 2 (this means either a detailed title or small remark about the content of the study was included). If there was a somewhat more detailed but short description about the study, the registration was coded as 3 and finally, all registrations that included a detailed description were coded as 4. In this way, we could compare the quality of the registrations in both groups and check for possible differences that could lead to different publication rates. 18\% of all registrations in the manually opened registrations and 16\% of all registrations in the automatically opened registration were empty, so that it was not clear what the goal or topic of the study was purely based on the registration. At least a minimal description was given for 36\% of the registrations in the manually opened registrations and 28\% in the automatically opened registration, meaning that although very brief, there were some details about the content of the study (e.g., a descriptive title). A more detailed short description was provided in 10\% of the cases in the manually opened registrations and 7\% of the cases in the automatically opened registration. Finally, most registrations seem to fall in the last group of extensive registrations (36\% and 48\% in the manually opened registrations and the automatically opened registration, respectively). These results are summarized in Table \ref{tab:table-quality}. The fact that similar percentages are found in manually opened registrations and the automatically opened registration shows that the level of detail in the registrations does not differ substantially between the two groups. Therefore, the difference in probability that we found a registration that was classified as manually opened, compared to classifications that were automatically opened, is not explained by a difference in the level of detail of the registrations.
